---
title: "Active Layers"
date: "11/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# Load the Required Packages
library(tidyverse)
library(sf)
library(sp)
library(rgdal)
library(raster)
library(dplyr)
library(rgeos)
library(scales)
library(fasterize)
library(dismo)
library(maptools)
library(sdmpredictors)
library(leaflet)
library(maps)
library(ncdf4)
library(marmap)
library(rnaturalearth)
library(dplyr)
library(ggmap)
#library(rmapshaper)

```


Set-Up for Downloading Data Using the "Maricultura" Google Drive File Stream
```{r}
# Create a Root to Extract Files 
if(Sys.info()["sysname"] == "Windows"){ #If operating system is "Windows" use G: Drive
  team_path <- "G:/"
} else { # If it is not (i.e. Mac), use the Google Drive File Stream
  team_path <- "/Volumes/GoogleDrive/"
}

#Create the Full File Path
path <- paste0(team_path, "Shared drives/Bren GP 2020 maricultura/Data/Raw_Data/Active_Data_Layers")

```


Read in Downloaded Data Layers from the Shared Drive: Bren GP 2020 maricultura/Data/Raw_Data/Active_Layers

Naming our Projection
```{r}
# Define CRS

crs_BRA <- "+proj=poly +lat_0=0 +lon_0=-54 +x_0=5000000 +y_0=10000000 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"

```

Exclusive Economic Zone, EEZ, marineregions.org
```{r}


# Read File
eez <- read_sf(dsn = path,
                layer = "eez_v10")

# Filtered to select only Brazil's EEZ
eez_BRA <- eez %>% 
  filter(ISO_Ter1 == "BRA")

# Reproject EEZ
eez_BRA <- st_transform(eez_BRA, crs_BRA)

# Plot Brazil EEZ
plot(eez_BRA$geometry)

# View CRS
st_crs(eez_BRA)


```

To Read in Bio-Oracle
Minimum and Maximum Sea-Surface Temperatures (SST), bio-oracle.org
```{r}
# Download Files
min_sst <- load_layers("BO_sstmin")
max_sst <- load_layers("BO_sstmax")

# View Histograms
#hist(min_sst)
#hist(max_sst)

# View Plots
#plot(min_sst)
#plot(max_sst)


# Reproject Temps to 5880 (Brazil's CRS)
min_sst_proj <-  projectRaster(min_sst, crs = crs_BRA)
max_sst_proj <-  projectRaster(max_sst, crs = crs_BRA)

# View CRS
st_crs(min_sst_proj)
st_crs(max_sst_proj)

# Crop to Brazil EEZ
max_sst_BR <- crop(max_sst_proj, eez_BRA)
min_sst_BR <- crop(min_sst_proj, eez_BRA)

# No Need to Reproject -> In Same CRS as EEZ


# Mask to Brazil EEZ
max_sst_BRA <- mask(max_sst_BR, eez_BRA)
min_sst_BRA <- mask(min_sst_BR, eez_BRA)


# View Cropped Histograms
#hist(max_sst_BRA)
#hist(min_sst_BRA)


# View Cropped Plots
#plot(max_sst_BRA)
#plot(min_sst_BRA)

```

Depth, gebco.net
```{r}
depth <- raster(paste0(path,"/gebco_2019_n7.045066_s-35.78779_w-54.58321_e-26.01452.tif"))


# View Histograms
#hist(depth)


# View Plots
#plot(depth)


# View CRS
#st_crs(depth)


# No Need to Reproject -> In Same CRS as EEZ
depth_proj <- projectRaster(depth, crs = crs_BRA)

# Resample to Bio-Oracle Cell Size (ATM Bio-Oracle Cell Size is the Standard)
depth_resample <- resample(depth_proj, min_sst_crop,method='ngb',progress='text')

# Crop to Brazil EEZ 
depth_crop <- crop(depth_resample, eez_BRA)

# Mask to Brazil EEZ
depth_mask <- mask(depth_crop, eez_BRA)


# Reclassification matrix for depth layer
rcl_mat_depth <- c(-Inf, -100, 0,
                   -100, -25, 1,
                   -25, Inf, 0)

# Reclassify the depth layer
depth_binary <- reclassify(depth_mask,rcl= rcl_mat_depth)


# Plot reclassified layer
plot(depth_binary)
```


Current Velocity, (Maximum Velocity at Minimum Depth), bio-oracle.org
```{r}
# Download File 
max_cv <- load_layers("BO2_curvelmax_bdmin")


# View Histograms
hist(max_cv)


# View Plots
plot(max_cv)


# View CRS
st_crs(max_cv)


# Crop to Brazil EEZ
current_BR <- crop(max_cv, eez_BRA)


# No Need to Reproject -> In Same CRS as EEZ


# Mask to Brazil EEZ
current_BRA <- mask(current_BR, eez_BRA)


# View Cropped Histogram
hist(current_BRA)


# View Cropped Plot
plot(current_BRA)



```


Marine Protected Areas (MPAs) - WWF
```{r}

# Create an Empty Raster 
empty_raster <- raster( extent, resolution = res)

# Download File
mpas <- read_sf(dsn = path,
                layer = "WDPA_Mar2018_marine-shapefile-polygons")


# Filter MPAs for Brazil
mpas_BRA <- mpas %>% 
  filter(ISO3 == "BRA")

# Plot MPAs
# plot(mpas_BR$geometry)

# View CRS
# st_crs(mpas_BR)


# Reproject MPAs
mpas_proj <- st_transform(mpas_BRA, crs = crs_BRA)

# No Need to Crop to Brazil EEZ

# Do Not Need to Resample because MPAs is a Polygon

# Rasterizing Steps for MPA Layer
# Create a Binary MPA Raster
mpas_binary <- rasterize(mpas_proj, empty_raster, field = 0, background = 1)

# Plot Reclassified MPA Layer
plot(mpas_binary)
freq(mpas_binary)

```

Reefs
```{r}

# Reefs: Setting Extent and Resolution
extent <- extent(eez_BRA)
res <-  res(min_sst_BRA)

# Create an Empty Raster 
empty_raster <- raster(extent, resolution = res, crs = crs_BRA)

# Read in, Reproject, and Simplify Reefs Layer and Remove Z Dimension
marine_ecosystems <- st_read(dsn = path, layer = "apzcm_alvo_ecossistemas_marinhos") %>% 
  st_transform(crs_BRA) %>% 
  ms_simplify(keep_shapes = TRUE) %>% 
  st_zm(drop = TRUE, what = "ZM")

# Create a Binary Reefs Rasters
reefs_binary <- rasterize(marine_ecosystems, empty_raster, field = 0, background = 1)

# View Plots
plot(reefs_binary)


```

---------Messy Beyond This Point-----------------


Wave Height
```{r}

# Download File
waves <- raster("G:/Shared drives/Bren GP 2020 maricultura/Data/Raw_Data/Active_Data_Layers/aq_waveheight.asc")
plot(waves)
```



No-Take Zones
```{r}




```





Artisanal Fishing Areas, WWF - Needs More Info - Maybe Better to Leave for Discussion
```{r}

# Download File
artisanal_areas <- read_sf(dsn = path,
                layer = "Artisanal_fishing_Areas")


# View Plots
plot(artisanal_areas$geometry)


# View CRS
st_crs(artisanal_areas)


# Reproject to EEZ
artisanal_rpj <- st_transform(artisanal_areas, CRS("+init=epsg:4326"))

# Crop to Brazil EEZ 
artisanal_BR <- crop(artisanal_rpj, eez_BRA)

# Mask to Brazil EEZ
depth_BRA <- mask(depth_BR, eez_BRA)

# Resample to Bio-Oracle Cell Size (ATM Bio-Oracle Cell Size is the Standard)
depth_BRA_res <- resample(depth_BRA, min_sst_BRA,method='ngb',progress='text')

# View Cropped Plot
plot(depth_BRA_res)

```


# Distance from Shore 
```{r}

# Read in Created .tif File from Distance to Shore.Rmd
dist_to_shore <- raster(paste0(path,"/distance_to_shore_coastline.tif"))

# Reclassify Matrix for Distance to Shore
rcl_matrix_dist_shore <- c(-Inf, 0, 0,
                           0, 46300, 1,
                           46300, Inf, 0)

# Reclassify Distance to Shore Layer
dist_shore_binary <- reclassify(distance_nonNA, rcl = rcl_matrix_dist_shore)


#Plot Reclassified Layers
plot(dist_shore_binary)

# View Distance Mask
plot(dist_to_shore)
# NOTE: This mask is distance to NON-LAND, since the land values are the NA. If we want to do distance to LAND, we would have to reverse the mask. It should really matter though, as long as numerically it is 25


# Set Maximum Shore Distance - JC's code
max_shore_distance <- 46300

shore_distance_mask <- dist_to_shore < 46300

plot(shore_distance_mask)

```


CRS
```{r}
# Use st_transform(layer, 5880)
# IT WORKS!!!!!!!!
st_transform(eez_BRA, 5880)
```





