---
title: "Data_Layers"
author: "Sandra Fogg"
date: "11/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# Load the Required Packages
library(tidyverse)
library(sf)
library(sp)
library(rgdal)
library(raster)
library(dplyr)
library(rgeos)
library(scales)
library(fasterize)
library(dismo)
library(maptools)
library(sdmpredictors)
library(maps)
library(ncdf4)
library(marmap)
```


Set-Up for Downloading Data Using the "Maricultura" Google Drive File Stream
```{r}
# Create a Root to Extract Files 
if(Sys.info()["sysname"] == "Windows"){ #If operating system is "Windows" use G: Drive
  team_path <- "G:/"
} else { # If it is not (i.e. Mac), use the Google Drive File Stream
  team_path <- "/Volumes/GoogleDrive/"
}

#Create the Full File Path
path <- paste0(team_path, "Shared drives/Bren GP 2020 maricultura/Data/Raw_Data/Active_Data_Layers")

```


Read in Downloaded Data Layers from the Shared Drive: Bren GP 2020 maricultura/Data/Raw_Data/Active_Layers

Exclusive Economic Zone, EEZ, marineregions.org
```{r}

# Read File
eez <- read_sf(dsn = path,
                layer = "eez_v10")

# Crop to Brazil
eez_BRA <- eez %>% 
  filter(ISO_Ter1 == "BRA")

# Plot Brazil EEZ
plot(eez_BRA$geometry)

# View CRS
st_crs(eez_BRA)

```

Minimum and Maximum Sea-Surface Temperatures (SST), bio-oracle.org
```{r}
# Download Files
min_sst <- load_layers("BO_sstmin")
max_sst <- load_layers("BO_sstmax")

# View Histograms
hist(min_sst)
hist(max_sst)

# View Plots
plot(min_sst)
plot(max_sst)

# View CRS
 st_crs(min_sst)
 st_crs(max_sst)


# Crop to Brazil EEZ
max_sst_BR <- crop(max_sst, eez_BRA)
min_sst_BR <- crop(min_sst, eez_BRA)


# No Need to Reproject -> In Same CRS as EEZ


# Mask to Brazil EEZ
max_sst_BRA <- mask(max_sst_BR, eez_BRA)
min_sst_BRA <- mask(min_sst_BR, eez_BRA)


# View Cropped Histograms
hist(max_sst_BRA)
hist(min_sst_BRA)


# View Cropped Plots
plot(max_sst_BRA)
plot(min_sst_BRA)

```

Depth, gebco.net
```{r}
# Read file
depth <- raster(paste0(path,"/gebco_2019_n7.045066_s-35.78779_w-54.58321_e-26.01452.tif"))


# View Histograms
hist(depth)


# View Plots
plot(depth)


# View CRS
st_crs(depth)


# No Need to Reproject -> In Same CRS as EEZ


# Crop to Brazil EEZ 
depth_BR <- crop(depth, eez_BRA)

# Mask to Brazil EEZ
depth_BRA <- mask(depth_BR, eez_BRA)

# Resample to Bio-Oracle Cell Size (ATM Bio-Oracle Cell Size is the Standard)
depth_BRA_res <- resample(depth_BRA, min_sst_BRA,method='ngb',progress='text')

# View Cropped Plot
plot(depth_BRA_res)

```


Current Velocity, (Maximum Velocity at Minimum Depth)
```{r}
# Download File 
max_cv <- load_layers("BO2_curvelmax_bdmin")


# View Histograms
hist(max_cv)


# View Plots
plot(max_cv)


# View CRS
st_crs(depth)

# Crop to Brazil EEZ
current_BR <- crop(max_cv, eez_BRA)


# Mask to Brazil EEZ
current_BRA <- mask(current_BR, eez_BRA)


# Resample to Bio-Oracle Cell Size


# View Cropped Histogram
hist(current_BRA)


# View Cropped Plot
plot(current_BRA)



```



Marine Protected Areas (MPAs)
```{r}
# Download File
mpas <- read_sf(dsn = path,
                layer = "WDPA_Mar2018_marine-shapefile-polygons")

# Reproject CRS
mpas_rpj <- st_transform(mpas, CRS("+init=epsg:5880"))


# Crop to Brazil - necessary?
#mpas_BRA <- crop(mpas_rpj, eez_BRA)


# Resample to Bio-Oracle Cell Size (ATM Bio-Oracle Cell Size is the Standard)
# Will not work because min_sst_BRA needs to be reprojected
mpas_BRA_res <- resample(mpas_rpj, min_sst_BRA,method='ngb',progress='text')


# Plot Brazil EEZ
#plot(mpas_rpj)
#Not sure if read in correctly, only 5 files in zip whereas other files zips have 8


#There is a distance function in raster- you feed a raster that has both values and NAs nd it returns raster that calculates distance to nearest non NA cell
#distance to shore

# set max_land_distance <- 25

#land_distance_mask <- land_distance < max_land_distance



```



Read in Bio-Oracle
```{r}
#Explore Datasets and Layer Names in the Package 
##Explore Datasets
list_datasets() 

##Explore Layers
list_layers() 

```



CRS
```{r}
proj4string(eez)
class(eez)

CRS("+init=epsg:5880")
#CRS arguments:
# +init=epsg:5880 +proj=poly +lat_0=0 +lon_0=-54 +x_0=5000000 +y_0=10000000
#+ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs 

eez_BRA <- eez %>% 
  filter(ISO_Ter1 == "BRA")
```




