---
title: "Growth Model"
author: "Anna Calle"
date: "1/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

three inputs for species:

- salmon
- gilthead
- cobia


Step 1. Defining values for coefficients/variables based on inputs

a1 = if (input$species = salmon){
coeff for salmon
}
else if (input$species = gilthead){
coeff for gilthead
}
else (input$species = cobia){
coeff for cobia
}

a2 = if (input$species = salmon){
coeff for salmon
}
else if (input$species = gilthead){
coeff for gilthead
}
else (input$species = cobia){
coeff for cobia
}

b1 = if (input$species = salmon){
coeff for salmon
}
else if (input$species = gilthead){
coeff for gilthead
}
else (input$species = cobia){
coeff for cobia
}

b2 = if (input$species = salmon){
coeff for salmon
}
else if (input$species = gilthead){
coeff for gilthead
}
else (input$species = cobia){
coeff for cobia
}

T0 =
if (input$species = salmon){
coeff for salmon
}
else if (input$species = gilthead){
coeff for gilthead
}
else (input$species = cobia){
coeff for cobia
}


Mean Sea-Surface Temperatures (SST), bio-oracle.org
```{r}
# Download Files
# mean_sst <- load_layers("BO2_tempmean_ss")

# Reproject to 5880 (Brazil's CRS)
# mean_sst_proj <-  projectRaster(mean_sst, crs = crs_BRA)

# View CRS
# st_crs(mean_sst_proj)

# Crop to Brazil EEZ
# mean_sst_crop <- crop(mean_sst_proj, eez_BRA)

# Mask to Brazil EEZ
# mean_sst_mask <- mask(mean_sst_crop, eez_BRA)

# Save raster
# writeRaster(mean_sst_mask, paste0(path, "/mean_sst_mask.tif"), overwrite = T)


# Read saved raster
mean_sst_mask <- raster(paste0(path,"/mean_sst_mask.tif"))
```



```{r}
# Overlay suitable raster and mean SST
suitable_sst <- overlay(mean_sst_mask, suitable, fun = function(x, y) {x * y})
plot(suitable_sst)
```






```{r}
# Defining variables for cobia
a1 = 0.0714
a2 = -0.1667
b1 = -1.5714
b2 = 5.3333
T0 = 29

# Create df with all values for variables
species_var_df <- data.frame(species = c(1, 2, 3),
                             a1 = c(0.0264, 0.026, 0.0714), 
                             a2 = c(-0.066, -0.0042, -0.1667), 
                             b1 = c(-0.0396,-0.0308, -1.5714), 
                             b2 = c(1.254, 0.1388, 5.3333), 
                             T0 = c(14, 25, 29))

# Select third row values (cobia)
cobia <- as.numeric(species_var_df[3,])
a1 <-  subset(species_var_df, species == "cobia", select = a1) %>% 
  as.numeric()

```



```{r}
# Process without making it into a function
# Convert zeros into NAs, otherwise all background would be less than T0
suitable_sst[suitable_sst == 0] <- NA 

# Separete cells into cells above and below optimal SST
cells_below_optimal <- suitable_sst < T0
plot(cells_below_optimal)

cells_above_optimal <-  suitable_sst >= T0
plot(cells_above_optimal)

# Apply growth equations
growth_below_optimal <- a1*cells_below_optimal*suitable_sst - b1*cells_below_optimal
growth_above_optimal <- a2*cells_above_optimal*suitable_sst + b2*cells_above_optimal

# Plot results of growth equations
plot(growth_below_optimal)
plot(growth_above_optimal)

# Add both rasters
growth_added <- growth_above_optimal + growth_below_optimal

# Plot final raster
plot(growth_added)

```




```{r}
# Function
growth_function = function (species_var, suitable_sst) {
  # Set variables from vector (starts at element 2 because element 1 is species name)
  a1 = species_var[2]
  a2 = species_var[3]
  b1 = species_var[4]
  b2 = species_var[5]
  T0 = species_var[6]
  
  # Convert zeros into NAs, otherwise all background would be less than T0
  suitable_sst[suitable_sst == 0] <- NA
  
  # Separete cells into cells above and below optimal SST
  cells_below_optimal <- suitable_sst < T0
  
  cells_above_optimal <-  suitable_sst > T0
  
  # Apply growth equations
  growth_below_optimal <- a1*cells_below_optimal*suitable_sst - b1*cells_below_optimal
  growth_above_optimal <- a2*cells_above_optimal*suitable_sst + b2*cells_above_optimal
  
  # Add both rasters
  growth_added <- growth_above_optimal + growth_below_optimal
}

# Apply function
cobia_growth <- growth_function(cobia, suitable_sst)
plot(cobia_growth)

```


