---
title: "Suitability"
author: "Anna Calle"
date: "11/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load required packages
library(rnaturalearthdata)
library(rnaturalearth)
library(sf)
library(raster)
library(ggplot2)
library(dplyr)
library(RColorBrewer)
```


Suitability 

- Depth: 25-100m
- Min sea surface temp: >22째C
- Max sea surface temp: <32째C
- Distance to shore: <25 nautical miles
- Current velocity: <1m/s
- Min dissolved oxygen: >4.41 mg/L (70.559 mmol m^3)

Defining variables
```{r}
min_depth <- -25 
max_depth <- -100
min_sst_value <- 22
max_sst_value <- 32
max_dist_shore <- 46300 #25 nautical miles converted to meters
max_cv_value <- 1
min_DO_value <- 70.559

```

Set-Up for Downloading Data Using the "Maricultura" Google Drive File Stream
```{r}
# Create a Root to Extract Files 
if(Sys.info()["sysname"] == "Windows"){ #If operating system is "Windows" use G: Drive
  team_path <- "G:/"
} else { # If it is not (i.e. Mac), use the Google Drive File Stream
  team_path <- "/Volumes/GoogleDrive/"
}

#Create the Full File Path
path <- paste0(team_path, "Shared drives/Bren GP 2020 maricultura/Data/Raw_Data/Active_Data_Layers")

```

CRS
```{r}
# Assign projection: SIRGAS 2000 / Brazil Polyconic
crs_BRA <- "+proj=poly +lat_0=0 +lon_0=-54 +x_0=5000000 +y_0=10000000 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
```

Data for graphs
```{r}
# Read in Brazil's EEZ
eez_BRA <- read_sf(dsn = path,
                layer = "eez_BRA")
# Brazil's outline in correct projection and cropped to the EEZ's extent
bound_BRA <- ne_countries(scale = 50, country = "Brazil", returnclass = "sf") %>%
  st_transform(crs_BRA) %>% 
  sf::st_crop( bound_BRA, y = extent(eez_BRA))


```

EEZ Raster
```{r}
# Read in 1's raster
raster_all_1 <- raster(paste0(path,"/raster_ones.tif"))

# Crop to EEZ
eez_all_1 <- crop(raster_all_1, eez_BRA)

# Save raster (to use in app)
writeRaster(eez_all_1, paste0(path, "/eez_all_1.tif"), overwrite = T)

# Make df
eez_all_1_df <- as.data.frame(eez_all_1, xy = T)

# Graph with Brazil's outline
eez_all_1_graph <- ggplot() +
    geom_raster(data = eez_all_1_df,
                mapping = aes(x = x, y = y, fill = as.factor(raster_ones))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", "Suitable", ""),
    values = c("#EFEFEF", "#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))
  
eez_all_1_graph
```


Reclassifying depth to have 1s only if it's in between 25-100m, and 0s otherwise
```{r}
# Read in file
depth_mask <- raster(paste0(path,"/depth_mask.tif"))

# Reclassification matrix for depth layer that makes NA background zeros, suitable cells 2, an unsuitable 1
rcl_mat_depth <- c(-Inf, max_depth, 1,
                   max_depth, min_depth, 2,
                   min_depth, 0, 1,
                   0, Inf, 0)

# Reclassify the depth layer
depth_binary_1 <- reclassify(depth_mask,rcl= rcl_mat_depth)

# Adding missing portion of EEZ using an raster cropped to the correct shape of the EEZ

# Overlay with 1's raster with the correct shape of the EEZ
depth_binary_2 <- overlay(depth_binary_1, eez_all_1, fun = function(a, b) {a + b})

# Reclassification matrix for depth layer
rcl_mat_depth_2 <- c(-Inf, 2.1, 0,
                   2.9, 3.1, 1)

# Reclassify the depth layer
depth_binary <- reclassify(depth_binary_2,rcl= rcl_mat_depth_2)

plot(depth_binary)

# Make df
depth_binary_df <- as.data.frame(depth_binary, xy = T)

# Graph with Brazil's outline
depth_binary_graph <-  ggplot() +
    geom_raster(data = depth_binary_df,
                mapping = aes(x = x, y = y, fill = as.factor(layer))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", "Suitable", ""),
    values = c("#EFEFEF", "#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

depth_binary_graph

```

Reclassify min SST layer to have 1s only if it is above 22째C, and 0s otherwise
```{r}
# Read in file
min_sst_mask <- raster(paste0(path,"/min_sst_mask.tif"))

# Reclassification matrix for min SST
rcl_matrix_min <- c( -Inf, min_sst_value, 0,
                min_sst_value, Inf, 1)

# Reclassify min SST
sst_binary_min <- reclassify(min_sst_mask, rcl = rcl_matrix_min)

# Plot reclassified layer
plot(sst_binary_min)

# Area (for presentation)
suitable_area(sst_binary_min)

# Make df
sst_binary_min_df <- as.data.frame(sst_binary_min, xy = T)

# Graph with Brazil's outline
sst_binary_min_graph <- ggplot() +
    geom_raster(data = sst_binary_min_df,
                mapping = aes(x = x, y = y, fill = as.factor(min_sst_mask))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", "Suitable", ""),
    values = c("#EFEFEF", "#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

sst_binary_min_graph

# Make df for min_sst_mask (for presentation)
min_sst_mask_df <- as.data.frame(min_sst_mask, xy = T)

# Graph min SST (for presentation)
min_sst_mask_graph <- ggplot() +
    geom_raster(data = min_sst_mask_df,
                mapping = aes(x = x, y = y, fill = min_sst_mask)) +
   scale_fill_distiller(palette = "Spectral",
                        guide = FALSE,
                        na.value="white") +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
   theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

min_sst_mask_graph


```

Reclassify max SST layer to have 1s only if it is less than 30째C, and 0s otherwise
```{r}
# Read in file
max_sst_mask <- raster(paste0(path,"/max_sst_mask.tif"))

# Reclassify matrix for max SST layer
rcl_matrix_max <- c( -Inf, max_sst_value, 1,
                max_sst_value, Inf, 0)

# Reclassify max SST layer
sst_binary_max <- reclassify(max_sst_mask, rcl = rcl_matrix_max)

# Plot reclassified layer
plot(sst_binary_max)

# Make df
sst_binary_max_df <- as.data.frame(sst_binary_max, xy = T)

# Graph with Brazil's outline
sst_binary_max_graph <- ggplot() +
    geom_raster(data = sst_binary_max_df,
                mapping = aes(x = x, y = y, fill = as.factor(max_sst_mask))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", ""),
    values = c("#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

sst_binary_max_graph

```

Reclassify max current velocity to have 1s only if it is less than 1m/s, and 0s otherwise
```{r}
# Read in file
max_cv_mask <- raster(paste0(path,"/max_cv_mask.tif"))

# Reclassification matrix for current layer
rcl_mat_current <- c(-Inf, max_cv_value, 1,
                   max_cv_value, Inf, 0)

# Reclassify the depth layer
current_binary <- reclassify(max_cv_mask ,rcl= rcl_mat_current)

# Plot reclassified layer
plot(current_binary)

# Make df
current_binary_df <- as.data.frame(current_binary, xy = T)

# Graph with Brazil's outline
current_binary_graph <- ggplot() +
    geom_raster(data = current_binary_df,
                mapping = aes(x = x, y = y, fill = as.factor(max_cv_mask))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", ""),
    values = c("#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

current_binary_graph

```

Reclassify distance to shore layer to have 1s only if it is less than 25nm, and 0s otherwise
```{r}
# Read in file
dist_shore <- raster(paste0(path,"/dist_shore.tif"))

# Reclassify matrix for distance to shore layer
rcl_matrix_dist_shore <- c( -Inf, 0, 0,
                            0, max_dist_shore, 1,
                            max_dist_shore, Inf, 0)

# Reclassify distance to shore layer
dist_shore_binary <- reclassify(dist_shore, rcl = rcl_matrix_dist_shore)

# Plot reclassified layer
plot(dist_shore_binary)

# Make df
dist_shore_binary_df <- as.data.frame(dist_shore_binary, xy = T)

# Graph with Brazil's outline
dist_shore_binary_graph <- ggplot() +
    geom_raster(data = dist_shore_binary_df,
                mapping = aes(x = x, y = y, fill = as.factor(dist_shore))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", "Suitable", ""),
    values = c("#EFEFEF", "#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

dist_shore_binary_graph

```

Reclassify DO layer to have 1s only if it is above 200.5 umol, and 0s otherwise
```{r}

# Units? \xbemol/m\x9f mol/ m3
# Read in file
DO_min_mask <- raster(paste0(path,"/DO_min_mask.tif"))

plot(DO_min_mask)

# Reclassification matrix for DO
rcl_matrix_DO <- c( -Inf, min_DO_value, 0,
                min_DO_value, Inf, 1)

# Reclassify DO min
DO_min_binary <- reclassify(DO_min_mask, rcl = rcl_matrix_DO)

# Plot reclassified layer
plot(DO_min_binary)

# Make df
DO_min_binary_df <- as.data.frame(DO_min_binary, xy = T)

# Graph with Brazil's outline
DO_min_binary_graph <- ggplot() +
    geom_raster(data = DO_min_binary_df,
                mapping = aes(x = x, y = y, fill = as.factor(DO_min_mask))) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", ""),
    values = c("#0077e6")) +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

DO_min_binary_graph
```

```{r}
##### Sig. wave height? #####
```

Overlay of all layers minus species specific layers for cobia (temperature and DO)
```{r}
# Overlay
all_layers_no_cobia <- overlay(
                       depth_binary,
                       current_binary,
                       dist_shore_binary,
                       mpas_binary,
                       reefs_binary,
                       reefs_artificial_binary,
                       og_pipeline_binary,
                       og_production_binary,
                       shipping_binary,
                       fun = function(a, b, c, d, e, f, g, h, i){a*b*c*d*e*f*g*h*i})

# Plot
plot(all_layers_no_cobia)

# Convert env. constrains raster to dataframe
all_layers_no_cobia_df <- as.data.frame(all_layers_no_cobia, xy = T) %>% 
  mutate(suitable= case_when(
    layer == 1 ~ "Suitable",
    layer != 1 ~ "Not Suitable"
  ))

# Create finalized graph
all_layers_no_cobia_graph <- ggplot() +
    geom_raster(data = all_layers_no_cobia_df,
                mapping = aes(x = x, y = y, fill = suitable)) +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", "Suitable", ""),
    values = c("#EFEFEF", "#0077e6")) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

all_layers_no_cobia_graph

# Area calculation
suitable_area(all_layers_no_cobia) # 9380.224 km2

```







Overlay of all Layers
```{r}
# Following presentation slides
all_layers <-  overlay(sst_binary_min,
                       sst_binary_max,
                       depth_binary,
                       current_binary,
                       dist_shore_binary,
                       DO_min_binary,
                       mpas_binary,
                       reefs_binary,
                       reefs_artificial_binary,
                       og_pipeline_binary,
                       og_production_binary,
                       shipping_binary,
                       fun = function(a, b, c, d, e, f, g, h, i, j, k, l){a*b*c*d*e*f*g*h*i*j*k*l})

# Plot
plot(all_layers)

# Convert env. constrains raster to dataframe
all_layers_df <- as.data.frame(all_layers, xy = T) %>% 
  mutate(suitable= case_when(
    layer == 1 ~ "Suitable",
    layer != 1 ~ "Not Suitable"
  ))

# Create finalized graph
all_layers_graph <- ggplot() +
    geom_raster(data = all_layers_df,
                mapping = aes(x = x, y = y, fill = suitable)) +
  scale_fill_manual(
    name = "", # Gives an empty title for the legend
    labels = c("Exclusive Economic Zone", "Suitable", ""),
    values = c("#EFEFEF", "#0077e6")) +
    geom_sf(data = bound_BRA, fill = "#DCDBE0") +
  theme_void() +
  theme(panel.grid.major = element_line(color = "white"))

all_layers_graph

# Area calculation
suitable_area(all_layers) # 9380.224 km

round(freq(all_layers, value = 1)*123.424, digits = 0) # resolution is 92.8 * 13.3

```



